Replication of Gantman et al. 2024

### 2024-02-20 manuscript.qmd
updating analysis

@@

@@

@@

subject_eeg <- eeg_data %>%
  filter(good_segment == TRUE) %>%
  filter(electrode %in% c("Cz", "Pz")) %>%
  filter(correct == TRUE) %>%
  group_by(subject, t, electrode, word_type, is_word) %>%
  summarize(v = mean(v)) %>%
  mutate(word_category = ifelse(word_type %in% c("fashion", "moral"), "category", "non-category"),
         category = ifelse(word_type %in% c("fashion", "non-fashion"), "fashion", "moral"))
```

```{r}
grand_average <- subject_eeg %>%
  group_by(t, electrode, word_category, category, is_word) %>%
  summarize(M = mean(v), SE = sd(v)/sqrt(n()))
```

>>>>

```{r}
#| label: Flip responses for subject 01
#| include: false

behavioral_data <- behavioral_data %>%
  mutate(correct = ifelse(subject_id == "01", !correct, correct))
```

@@

```{r}
#| label: model the GEE

library(gee)

m <- gee(correct ~ word_category,
    id = subject_id,
    subset = is_word == TRUE & category == "moral",
    data = behavioral_data_test_set,
    family = binomial,
    corstr = "exchangeable")

summary(m)
```

@@

```{r}
#| label: Flip subject 01s responses
#| include: false

eeg_data <- eeg_data %>%
  mutate(correct = ifelse(subject == "01", !correct, correct))
```

@@

subject_eeg <- eeg_data %>%
  filter(good_segment == TRUE) %>%
  filter(electrode %in% c("Cz", "Pz")) %>%
  filter(correct == TRUE) %>%
  group_by(subject, t, electrode, word_type, is_word) %>%
  summarize(v = mean(v), n=n()) %>%
  mutate(word_category = ifelse(word_type %in% c("fashion", "moral"), "category", "non-category"),
         category = ifelse(word_type %in% c("fashion", "non-fashion"), "fashion", "moral"))
```

```{r}
grand_average <- subject_eeg %>%
  group_by(t, electrode, word_category, category, is_word) %>%
  summarize(M = weighted.mean(v, n), SE = sd(v)/sqrt(n()))
```
